Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-05-11 papers/intro_paper/intro_paper.tex
minor

We additionally investigate the effects of erroneously assuming that
an underlying non-GR signal can be well-described by a GR one. We do
this by estimating the parameters of our non-GR signals using the GR
waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
resulting one- and two-dimensional posteriors are shown in the right
panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
GW150914-like (top) and GW190521-like (bottom) signals
respectively. For both signals, we find the 2D $\SEOB$ estimates are
markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
this impact on the estimation of the GR parameters $\bxigr$ by changing the
magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. This gives us 
confidence that the $\pSEOB$ model can accurately measure QNM 
properties without biasing measurements of inspiral quantities, like masses and spins. 
\textcolor{blue}{As we increase the deviation, the remnant object rings down at a higher frequency and damping time. The resulting $\pSEOB$ signal is longer than the GR ($\SEOB$) prediction. When we try to fit the $\SEOB$ model to this signal (left column of Fig.~\ref{fig:gr_ngr_comparison}), the template tries to fit parameters appropriate for a longer signal, i.e., smaller masses and spins. Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.}
To compute the samples of the final mass and spin in the last row, we start from the samples
of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b}),
and then invert them using the fitting formula in Ref.~\cite{Berti:2005ys}.
The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
three unique sets of values for $(M_f,\chi_f)$. These predicted values are correctly 
recovered by the $\pSEOB$ waveform (bottom-right plot in Fig.~\ref{fig:gr_ngr_comparison}),
leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$.

>>>>

We additionally investigate the effects of erroneously assuming that
an underlying non-GR signal can be well-described by a GR one. We do
this by estimating the parameters of our non-GR signals using the GR
waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
resulting one- and two-dimensional posteriors are shown in the right
panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
GW150914-like (top) and GW190521-like (bottom) signals
respectively. For both signals, we find the 2D $\SEOB$ estimates are
markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
this impact on the estimation of the GR parameters $\bxigr$ by changing the
magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. This gives us 
confidence that the $\pSEOB$ model can accurately measure QNM 
properties without biasing measurements of inspiral quantities, like masses and spins. 
\textcolor{blue}{As we increase the deviation, the remnant object rings down at a higher frequency and damping time. The resulting $\pSEOB$ signal is longer than the GR ($\SEOB$) prediction. When we try to fit the $\SEOB$ model to this signal (left column of Fig.~\ref{fig:gr_ngr_comparison}), the template tries to fit parameters appropriate for a longer signal, i.e., smaller masses and spins. Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.}
To compute the samples of the final mass and spin in the last row, we start from the samples
of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b}),
and then invert them using the fitting formula in Ref.~\cite{Berti:2005ys}.
The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
three unique sets of values for $(M_f,\chi_f)$. These predicted values are correctly 
recovered by the $\pSEOB$ waveform (bottom-right plot in Fig.~\ref{fig:gr_ngr_comparison}),
leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$).
